Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-10 main.tex
general updates and corrections

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*}
        \| \Jacobian \varphi \|
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \Czwei{n} \cdot 
        \kappa(T) 
        \diam(T)^{-1}
        ,
        \\
        \alpha(T)
        \leq 
        \Csechs{n}
        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        \kappa(T)
        .
    \end{gather*}
    Here,
    \begin{align*}
        \Ceins{n} \leq \sqrt{n},
        \quad 
        \Czwei{n} \leq \sqrt{ 2n/(n-1)^{n-1} },
        \quad 
        \Csechs{n} \leq \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        . 
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
%     By a result of Hong and Pan,
%     \begin{align*}
%         \frac{ \sigma_{n} }{ \sigma_{1} }
%         \geq 
%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ \| \Jacobian\varphi \| }
%         \sigma_{1}^{-1}
%         \geq 
%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ n \sigma_{1} }
%         \sigma_{1}^{-1}
%         .
%     \end{align*}
    By a result of Yu and Gu \cite{yisheng1997note},
    \begin{align*}
        \frac{ \sigma_{n} }{ \sigma_{1} }
        &\geq 
        \det(\Jacobian\varphi)
        \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
        \sigma_{1}^{-1}
%         \geq 
%         (n-1)^{\frac{n-1}{2}}
%         \det(\Jacobian\varphi)
%         \left( \frac{1}{ \diam(T)^{n-1} } \right)^{}
%         \frac{1}{\sqrt{n} \diam(T)}
%         \\&
%         \geq 
%         \frac{1}{\sqrt{n}}
%         (n-1)^{\frac{n-1}{2}}
%         \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
        \geq 
        \sqrt{\frac{ (n-1)^{n-1} }{n} }
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
        .
    \end{align*}
    Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. 
%     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
%     \begin{gather*}
%         \diam(T) 
%         \leq 
%         \sqrt{2} \sigma_1 
%         \leq 
%         \sqrt{2} 
%         \frac{ \sigma_1^{n} }{ { \det(\Jacobian\varphi) } } 
%         \sigma_n
%         \leq 
%         \sqrt{2n^{n}} 
%         \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)
%         \sigma_n
%         .
%     \end{gather*}
%     The desired result is thus evident. 
\end{proof}

@@

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \kappa(T_1)
        \diam(F)
        ,
        \qquad 
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \kappa(T_1) \kappa(T_2)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \Cdrei{n}
        \kappa(T_2)^{-1} \kappa(T_1) 
        % \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
    Here, $\Cdrei{n} \leq \Ceins{n} \Czwei{n}$. 
\end{lemma}

@@

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation of an $n$-dimensional domain. 
    Let $S \in \calT$ be a simplex of dimension $k < n$,
    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
    and let 
    \begin{align*}
        U := |\patch_{\calT}(S)| \setminus T.
    \end{align*}
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi : T \rightarrow U
    \end{align*}
    satisfying
    \begin{gather*}
        \| \Jacobian\Xi \|          \leq \Cvier{n}{k}(\calT),
        \quad 
        \| \Jacobian\Xi^{-1} \|     \leq \Cfive{n}{k}(\calT),
        \\
        \| \det\Jacobian\Xi \|      \leq \Cdetvier{n}{k}(\calT),
        \quad 
        \| \det\Jacobian\Xi^{-1} \| \leq \Cdetfive{n}{k}(\calT),
    \end{gather*}
    where the constants on the right-hand sides are as stated in the proof. 
\end{theorem}
\begin{proof}
    We derive the estimate in several steps. 
    \begin{itemize}
        \item 
        Without loss of generality, the barycenter of $S$ is the origin. 
        % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        %We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        %So $J$ is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
        Note that $J$ is the union of exactly those faces of $T$ that contain $S'$.

@@

        \item 
        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$.
        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
        be affine reference transformations
        that agree on the vertices common to $K$ and $K'$.
        We then define 
        \begin{align*}
            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
        \end{align*}
        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
        \begin{align*}
            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
            \\
            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
        \end{align*}
        By construction, the mapping preserves volumes:
        \begin{align*}
            |\det( \Jacobian      \Theta_{|K} )|
            = 
            |\det( \Jacobian^{-1} \Theta_{|K} )|
            =
            1
            .
        \end{align*}
        We want to characterize the singular values of this transform. 
        We $h_z \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
        We can write
        \begin{align*}
            \Theta_{|K}(x) 
            = 
            x
            - 
            2 \hat z_{S'} \frac{\langle \hat h_z, x \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
            .
        \end{align*}
        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $\hat h_z$,
        and that it equals $-z_{S'}$ when $x = z_{S'}$.
%         and when $x = z_{S'}$, then 
%         \begin{align*}
%             -z_{S'} 
%             =
%             z_{S'}
%             - 
%             2 \hat z_{S'} \frac{\langle \hat h_z, z_{S'} \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
%             .
%         \end{align*}
        If we orthogonally decompose $z_{S'} = h_z + b_z$, then 
        \begin{align*}
            \Theta_{|K}( h_z ) 
            &= 
            h_z
            - 
            2 z_{S'} \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle}
            %\\&
            = 
            h_z
            - 
            2 z_{S'}
            %\\&
            = 
            - h_{z}
            - 
            2 b_{z}
            .
        \end{align*}
        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
        Then $\| h_z \| = \cos(\beta) \|z_{S'}\|$ and $\| b_z \| = \sin(\beta) \|z_{S'}\|$. 
        We study the singular values of the matrix 
        \begin{align*}
            B 
            := 
            \begin{pmatrix}
            -1                 & 0
            \\ 
            -2 \|b_z\|/\|h_z\| & 1
            \end{pmatrix}
            =
            \begin{pmatrix}
            -1             & 0
            \\ 
            -2 \tan(\beta) & 1
            \end{pmatrix}
            .
        \end{align*}
        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
        Its square roots are the desired singular values of $B$:
        \begin{align*}
            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + \tan(\beta) \sqrt{ 4\tan(\beta)^2 + 4 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
            ,
            \\
            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - \tan(\beta) \sqrt{ 4\tan(\beta)^2 + 4 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
            .
        \end{align*}
        \begin{align*}
            \lambda
        \end{align*}
        These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$. 
        They are monotonely increasing and decreasing, respectively, in $\tan(\beta)$.

%         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
        By the definition of the tangent, $\tan(\beta) \leq \| b_{z} \| / \| h_{z} \|$, and we know $\|b_z\| \leq \|z_{S'}\|$. 
        Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
        which is also a face of $T$. Then $(n-k) h_{z}$ is the height vector of $F_{z}$ in $T$. 
        Thus 
        \begin{align*}
            \frac{ \| b_{z} \| }{ \| h_{z} \| }
            = 
            \frac{ \| b_{z} \| }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            = 
            \frac{ \| b_{z} \| \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
            \leq 
            \frac{ n-k-1 }{n!}
            \cdot 
            \frac{ \diam(T)^{n} }{ \vol(T) }
            :=
            \beta_T
            .
        \end{align*}
        This establishes bounds on the singular values of the transformation in terms of the mesh geometry. 
        We write 
        \begin{align*}
            \beta_T 
            := 
%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
%             \geq 
            \sqrt{ 
                1 + (n-k)^{2} \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
            } 
            + 
            (n-k) \frac{ \diam(T)^{n} }{ n! \vol(T) }            
            .
        \end{align*}

@@

        \item 
        We define a mapping $ \Xi : T \rightarrow U = \overline{\patch_{\calT}(S) \setminus T}$ by setting 
        \begin{align*}
            \Xi := \Psi \circ \Theta.
        \end{align*}
        It preserves the interface from $T$ onto $U$. We briefly recapitulate why it is bi-Lipschitz.

        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
        After application of a piecewise linear Lipschitz mapping, 
        we can assume that $|\calK|$ is convex without loss of generality. 
        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$. 
        By an application of Rademacher's theorem, we conclude that $\calK$ is bi-Lipchitz.

>>>>

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{gather*}
        \| \Jacobian \varphi \|
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \Czwei{n} \cdot 
        \kappa(T) 
        \diam(T)^{-1}
        ,
        \\
        \alpha(T)
        \leq 
        \Cdrei{n}
        % \sqrt{ \frac{n}{ (n-1)^{n-1} } }
        \kappa(T)
        .
    \end{gather*}
    Here,
    \begin{align*}
        \Ceins{n} \leq \sqrt{n},
        \quad 
        \Czwei{n} \leq          \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}, 
        \quad 
        \Cdrei{n} \leq \sqrt{n} \left( \frac{n}{n-1} \right)^{\frac{n-1}{2}}
        . 
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
    By a result of Hong and Pan \cite{hong1992lower},
    \begin{align*}
        \sigma_{n}
        &\geq 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n-1} }
        = 
        \left( \frac{n-1}{n} \right)^{\frac{n-1}{2}}
        \frac{ n! \vol(T) }{ \diam(T)^{n-1} }
        .
    \end{align*}
%     To get the second inequality, we multiple the last term by $\sigma_{1} / ( \sqrt{n} \diam(T) ) \leq 1$.
    The second inequality follows. 
    To get the third inequality, we divide both sides by $\sigma_{1}$ and use $\sigma_{1} \leq \sqrt{n} \diam(T)$.

%     By a result of Yu and Gu \cite{yisheng1997note},
%     \begin{align*}
%         \frac{ \sigma_{n} }{ \sigma_{1} }
%         &\geq 
%         \det(\Jacobian\varphi)
%         \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
%         \sigma_{1}^{-1}
%         \geq 
%         \left( \frac{n-1}{n^{2}} \right)^{\frac{n-1}{2}}
%         \det(\Jacobian\varphi)
%         \left( \frac{1}{ \diam(T)^{n-1} } \right)^{}
%         \frac{1}{\sqrt{n} \diam(T)}
%         \\&
%         \geq 
%         \left( \frac{n-1}{n^{2}} \right)^{\frac{n-1}{2}}
%         \frac{1}{\sqrt{n}}
%         \frac{ n! \vol(T) }{ \diam(T)^{n} }
%         .
%     \end{align*}
%     Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. % THIS IS OPTIMAL
%     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
%     \begin{gather*}
%         \diam(T) 
%         \leq 
%         \sqrt{2} \sigma_1 
%         \leq 
%         \sqrt{2} 
%         \frac{ \sigma_1^{n} }{ { \det(\Jacobian\varphi) } } 
%         \sigma_n
%         \leq 
%         \sqrt{2n^{n}} 
%         \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)
%         \sigma_n
%         .
%     \end{gather*}
%     The desired result is thus evident. 
\end{proof}

@@

\todo{Tighter estimate via geometry}
\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \kappa(T_1)
        \diam(F)
        ,
        \qquad 
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \kappa(T_1) \kappa(T_2)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \Cvier{n}
        \kappa(T_2)^{-1} \kappa(T_1) 
        % \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
    Here, $\Cvier{n} \leq \Ceins{n} \Czwei{n}$. 
\end{lemma}

@@

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation of an $n$-dimensional domain. 
    Let $S \in \calT$ be a simplex of dimension $k < n$,
    let $T \in \patch_{\calT}(S)$ be of dimension $n$,
    and let 
    \begin{align*}
        U := \overline{ |\patch_{\calT}(S)| \setminus T },
        \qquad 
        {\Gamma_I} := U \cap T,
        \qquad 
        {\Gamma_J} := \overline{ \partial T \setminus \partial U }.
    \end{align*}
    \begin{enumerate}
    \item 
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi_{1} : T \rightarrow U
    \end{align*}
    which is the identity along ${\Gamma_I} = T \cap U$ and which satisfies the upper bounds 
    \begin{gather*}
        \| \Jacobian\Xi_{1} \|          \leq \Cfive{n}{k}(\calT),
        \quad 
        \| \Jacobian\Xi_{1}^{-1} \|     \leq \Csechs{n}{k}(\calT),
        \\
        \| \det\Jacobian\Xi_{1} \|      \leq \Cdetfive{n}{k}(\calT),
        \quad 
        \| \det\Jacobian\Xi_{1}^{-1} \| \leq \Cdetsechs{n}{k}(\calT),
    \end{gather*}
    where the constants on the right-hand sides are as stated in the proof. 
    \item 
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi_{2} : T \rightarrow U
    \end{align*}
    which is the identity along $\partial U \setminus \partial T$ and which satisfies the upper bounds 
    \begin{gather*}
        \| \Jacobian\Xi_{2} \|          \leq \Csieb{n}{k}(\calT),
        \quad 
        \| \Jacobian\Xi_{2}^{-1} \|     \leq \Cacht{n}{k}(\calT),
        \\
        \| \det\Jacobian\Xi_{2} \|      \leq \Cdetsieb{n}{k}(\calT),
        \quad 
        \| \det\Jacobian\Xi_{2}^{-1} \| \leq \Cdetacht{n}{k}(\calT),
    \end{gather*}
    where the constants on the right-hand sides are as stated in the proof. 
    \end{enumerate}
\end{theorem}
\begin{proof}
    We derive the estimate in several steps. 
    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
    \begin{itemize}
        \item 
        Without loss of generality, the barycenter $z_{S}$ of $S$ is the origin. 
        % Let $I := U \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        %We let ${\Gamma_J} \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        %So ${\Gamma_J}$ is within the boundary of the star $|\patch_{\calT}(S)|$ and is disjoint from $S$.
        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$.
        Note that ${\Gamma_J}$ is the union of exactly those faces of $T$ that contain $S'$,
        whereas ${\Gamma_I} = U \cap T$ is the union of exactly those faces of $T$ that contain $S$.

@@

        \item 
        We introduce a new mapping $\Theta : |\calR| \rightarrow |\calR^c|$ as follows.
        Let $K \in \calR$ be an $n$-simplex and $K' \in \calR^{c}$ be constructed from $K$.
        We let $A_{K} : \Delta^{n} \rightarrow K$ and $A_{K'} : \Delta^{n} \rightarrow K'$
        be affine reference transformations
        that agree on the vertices common to $K$ and $K'$.
        We then define 
        \begin{align*}
            \Theta_{|K} := A_{K'} \circ A_{K}^{-1}.
        \end{align*}
        Notice that $A_{K'}$ and $A_{K}$ have the same singular values. Thus
        \begin{align*}
            \| \Jacobian \Theta_{|K}      \| &\leq \| A_{K'} \| \cdot \| A_{K}^{-1} \| \leq \kappa(A_{K}),
            \\
            \| \Jacobian \Theta_{|K}^{-1} \| &\leq \| A_{K'}^{-1} \| \cdot \| A_{K} \| \leq \kappa(A_{K}).
        \end{align*}
        By construction, the mapping preserves volumes:
        \begin{align*}
            |\det( \Jacobian      \Theta_{|K} )|
            = 
            |\det( \Jacobian^{-1} \Theta_{|K} )|
            =
            1
            .
        \end{align*}
        We want to characterize the singular values of this transform. 
        We $h_z \in \bbR^{n}$ be the height vector of $z_{S'}$ inside the simplex $K$.
        We can write
        \begin{align*}
            \Theta_{|K}(x) 
            = 
            x
            - 
            2 \hat z_{S'} \frac{\langle \hat h_z, x \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
            .
        \end{align*}
        Indeed, we check that the right-hand side equals $x$ whenever $x$ lies in the plane orthgonal to $h_z$,
        and that it equals $-z_{S'}$ when $x = z_{S'}$.
%         and when $x = z_{S'}$, then 
%         \begin{align*}
%             -z_{S'} 
%             =
%             z_{S'}
%             - 
%             2 \hat z_{S'} \frac{\langle \hat h_z, z_{S'} \rangle}{\langle \hat h_z, \hat z_{S'} \rangle}
%             .
%         \end{align*}
        If we orthogonally decompose $z_{S'} = h_z + b_z$, then 
        \begin{align*}
            \Theta_{|K}( h_z ) 
            &= 
            h_z
            - 
            2 z_{S'} \frac{\langle h_z, h_z \rangle}{\langle h_z, z_{S'} \rangle}
            = 
            h_z
            - 
            2 z_{S'} \frac{\langle h_z, z_{S'} \rangle}{\langle h_z, z_{S'} \rangle}
            %\\&
            = 
            h_z
            - 
            2 z_{S'}
            %\\&
            = 
            - h_{z}
            - 
            2 b_{z}
            .
        \end{align*}
        Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
        Then $\| h_z \| = \cos(\beta) \|z_{S'}\|$ and $\| b_z \| = \sin(\beta) \|z_{S'}\|$. 
        We study the singular values of the matrix 
        \begin{align*}
            B 
            := 
            \begin{pmatrix}
            -1                 & 0
            \\ 
            -2 \|b_z\|/\|h_z\| & 1
            \end{pmatrix}
            =
            \begin{pmatrix}
            -1             & 0
            \\ 
            -2 \tan(\beta) & 1
            \end{pmatrix}
            .
        \end{align*}
        We compute the eigenvalues of the symmetric matrix $B^{\ast} B$. 
        Its square roots are the desired singular values of $B$:
        \begin{align*}
            \sigma_{\max} = \sqrt{ 2\tan(\beta)^2 + 1 + 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } + \tan(\beta)
            ,
            \\
            \sigma_{\min} = \sqrt{ 2\tan(\beta)^2 + 1 - 2 \tan(\beta) \sqrt{ \tan(\beta)^2 + 1 } } = \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta)
            .
        \end{align*}
        They are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
        These are also the maximal and minimal singular values of $\Jacobian\Theta_{|K}$,
        whereas all its other singular values equal $1$.

%         Let $\beta$ be the angle between $z_{S'}$ and $h_{z}$. 
        By the definition of the tangent, $\tan(\beta) \leq \| b_{z} \| / \| h_{z} \|$, and we know $\|b_z\| \leq \|z_{S'}\|$. 
        Let $F_{z} \subseteq K$ be the face opposite to $z_{S'}$,
        which is also a face of $T$. Then $(n-k) h_{z}$ is the height vector of $F_{z}$ in $T$. 
        Thus 
        \begin{align*}
            \frac{ \| b_{z} \| }{ \| h_{z} \| }
            = 
            \frac{ \| b_{z} \| }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            = 
            \frac{ \| b_{z} \| \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
            \leq 
            \frac{ n-k }{n!}
            \cdot 
            \frac{ \diam(T)^{n} }{ \vol(T) }
            .
        \end{align*}
        This establishes bounds on the singular values of the transformation. 
        We write 
        \begin{align*}
            \beta_T 
            := 
%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
%             \geq 
            \sqrt{ 
                1 + (n-k)^{2} \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
            } 
            + 
            (n-k) \frac{ \diam(T)^{n} }{ n! \vol(T) }            
            .
        \end{align*}

        \item 
        We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Phi$.
        We construct a bi-Lipschitz mapping 
        \begin{align*}
            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}
        \end{align*}
        and analyze its properties. The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
        will define the required mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
        which will be bi-Lipschitz and the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.

        We write $h_{z}$ for the height of $z_{S'}$ within $K$.
        Given $x \in K \cup K^{c}$, we have a unique representation
        \begin{align*}
            x = t z_{S} + x^{\perp}, \quad t \in [-1,1], \quad x^{\perp} \in K \cap K^{c}.
        \end{align*}
        Notice that 
        \begin{align*}
            t = \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
            .
        \end{align*}
        Based on that observation, we define 
        \begin{align*}
            \Phi_{K}(x) := x - \frac 1 2 \left( \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - 1 \right) z_{S'}
            .
        \end{align*}
        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
        that satifies the desired mapping properties. 
        It remains to analyze its Jacobian to get explicit estimates.

        We have an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$.
        With that,
        \begin{align*}
            \Jacobian \Phi_{K}(x)
            &=
            \Id 
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle }  
            z_{S'} \otimes h_{z}^{t}
            \\
            &=
            \Id 
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
            h_{z} \otimes h_{z}^{t}
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
            b_{z} \otimes h_{z}^{t}
            \\
            &=
            \Id 
            - 
            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 
            h_{z} \otimes h_{z}^{t}
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
            b_{z} \otimes h_{z}^{t}
            \\
            &=
            \Id 
            - 
            \frac{1}{ 2 } 
            \hat h_{z} \otimes \hat h_{z}^{t}
            - 
            \frac{ \|b_z\| }{ 2 \| h_{z} \| } 
            \hat b_{z} \otimes \hat h_{z}^{t}
            .
        \end{align*}
        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
        Hence $\tan(\beta) = \| b_z \| / \| h_z \|$. It remains to study the singular values of the matrix 
        \begin{align*}
            C 
            = 
            \frac 1 2 
            \begin{pmatrix}
                -1 & 0 
                \\
                -\tan(\beta) & 2 
            \end{pmatrix}
        \end{align*}
        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
        \begin{align*}
            \sigma_{\max} 
            = 
            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
            =
            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
            ,
            \\
            \sigma_{\min} 
            = 
            \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
            =
            \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
            .
        \end{align*}
        These are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Phi_{K}$, the remaining eigenvalues being equal to $1$. 
%         Upon close inspection, we see that 
%         \begin{align*}
%             \sigma_{\max} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
%             ,
%             \\
%             \sigma_{\min} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
%             .
%         \end{align*}
        These are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
        Moreover, $\sigma_{\max} \sigma_{\min} = 1/2$. 
        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
        Similar as above, we use the upper bound 
        \begin{align*}
            \tan(\beta) = \frac{\|b_z\|}{\|h_z\|} \leq (k+1) \mu(T).
        \end{align*}
        We conclude that 
        \begin{gather*}
            \| \Jacobian\Phi_{K} \| 
            \leq 
            \frac 1 4 \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \mu(T)^2 }
            ,
            \\
            \| \Jacobian\Phi_{K}^{-1} \| 
            \leq 
            \frac 1 2 \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \mu(T)^2 }
            ,
            \\
            \det \Jacobian\Phi = \frac 1 2 
            .
        \end{gather*}
        This finishes the discussion of the transformation $\Phi$.

@@

        \todo{TODO: Integrate the following paragraph and make it two-sided.}
        We have shown that $\Psi$ and $\Psi^{-1}$ are piecewise Lipschitz over some essentially disjoint closed partitions over their respective domains.
        It remains to show both are Lipschitz, which we illustrate for $\Psi$, the argument for $\Psi^{-1}$ being analogous. 
        Rademacher's theorem then shows that both have essentially bounded weak Jacobians almost everywhere.

        We show that every function that is piecewise Lipschitz with respect to the triangulation $\calK$ must be Lipschitz over all of $|\calK|$. 
        We use a technique similar to Lemma~\ref{lemma:stars_are_shellable}. 
        After application of a piecewise linear Lipschitz mapping, 
        we can assume that $|\calK|$ is convex without loss of generality. 
        Any function piecewise Lipschitz with respect to $\calK$ must be Lipschitz over $|\calK|$.
